Nix for Polyglot, Reproducible Data Science Workflows

### 2025-10-28 paper.qmd
precision

A further advantage is that packages built by [Nix]{.pkg} act as universal
binaries across any Linux system where [Nix]{.pkg} is installed. This “build
once, run anywhere” property has long been solved by [Nix]{.pkg}, and is now
being revisited by Posit through its initiative to provide portable CRAN
binaries [@posit_portable_r_binaries].

>>>>

A further advantage is that packages built by [Nix]{.pkg} act as universal
binaries across any Linux system (on the same architecture) where [Nix]{.pkg} is
installed. This “build once, run anywhere” property has long been solved by
[Nix]{.pkg}, and is now being revisited by Posit through its initiative to
provide portable CRAN binaries [@posit_portable_r_binaries].
